---
title: "Cabbages"
author: "Juan Padilla"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: There is no difference in VitC contents between C39 and C52 cultivation methods.

$H_A$: There is a difference between VitC content based on the cultivation method of c39 and c52.

# Methods


<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
We are explaining the content of the VitC variable (numerical) by observing the cultivation variable (categorical). We will be utilizing the T test in order to compare the mean averages of c39 and c52 vitamin c groups.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
plot(VitC~Cult,data=veggy)
```

In the box plot you can see the response of Vitc 39 and 52. In this experiment you can see that c39 had the lower range in VitC content and as well as a lower mean average. The c52 cultivation method showed to have a higher Vit C content.
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
favstats(VitC~Cult,data=veggy)
```

The c39 cultivation content showed to have a minimum of 41 Vit C content as opposed to c52 having a 47 VitC content. The max of c39 had a 68 while c52 had a max of 84. C39 had a median of 51.0 while c52 had a median of 64.5. The mean for c39 is 51.5 while c52 had a mean of 64.5 The c52 showed higher results in its cultivation methods.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```
The p value of the T Test expirement is 0.000000003405. The p value is so low that the chances of it happening mean we can reject the null hypothesis. 
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

In this expirement we were trying to determine which method of cultivation in cabbages produced a higher content level of vitamin C. Based on our T test results, we can clearly see there is a difference in VitC content based on the cultivation method involved between c39 and c52. C52 had a higher numerical threshold of vitamin C, in terms of maximum, minimum, median, and even mean.
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

